---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# myrror

<!-- badges: start -->

[![R-CMD-check](https://github.com/giorgiacek/myrror/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/giorgiacek/myrror/actions/workflows/R-CMD-check.yaml) <!-- badges: end -->

A R package to compare data frames in R. 
The assumption is that the user wants the two data frames to be the same. 
`myrror()` highlights the differences between values. When there is no difference, the comparison is "successful". 


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("giorgiacek/myrror")
```
## Usage

The main function is `myrror()`, which goes through each single step of the comparison:

```{r}
library(myrror)
myrror(iris, iris_var1)
```

## Auxiliary functions

The auxiliary functions go through a specific step of the comparison, and can be used independently:

-   `compare_type()`: compares the type of shared columns.

-   `compare_values()`: compares the values of shared columns.

-   `extract_diff_values()`: extract the values that are different between two data frames, returns a list of data frames with the differences, one for each variable.

-   `extract_diff_table()`: extract the values that are different between two data frames, returns a data.table with all differences.

See more in the [Get started](https://giocek.github.io/myrror/articles/myrror.html) vignette.
