---
title: "myrror"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myrror}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# build_rmd("vignettes/myrror.Rmd")
```

```{r setup}
library(myrror)
```

## Overview

`myrror` is a package that helps you compare two data frames.

It has three types of functions:

1.  **Complete comparison**: `myrror()`, the "workhorse" function which will go through a complete comparison of two datastes.

2.  **Partial comparison**:

-   `compare_type()`: Compares the types of the columns in the two data frames.

-   `compare_values()`: Compares the values of the columns in the two data frames.

3.  **Extract differences**: two functions which allow you to access the rows that differ in values between the two data frames.

-   `extract_diff_values()`: Returns the differences in a list format, one table per variable.
-   `extract_diff_table()`: Returns the differences in a table format, all variables.

