---
title: "Extract Different Values"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(myrror)
library(DT)
```

This article looks at a series of workflows for the function `extract_diff_values()`. At its core, this function does the following:

1.  Sets up the two data frames (`dfx` and `dfy`) for comparison:
    -   Pairs rows based on the keys provided (given by the user using the `by` , `by.x`, `by.y` arguments, or by row number).
    -   Pairs columns based on the column names.
2.  Runs the comparison between shared rows and shared columns only.
3.  Returns a list of `data.table`s, one per variable, with the values of a given variable in `dfx` and `dfy` side-by-side.

This is a basic example of the function output when run in default mode, with `output = "simple"` :

```{r basic-example}
output <- extract_diff_values(iris, iris_var1, output = "simple")
str(output, max.level = 1)

```

What the console prints out should
