---
title: "Myrror Process Flow"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(myrror)
```

## With keys supplied

If keys (`by` or `by.x` and `by.y`) are supplied by the user, `myrror()` will first check whether the keys uniquely identify the dataset:

### Identified

If the keys are supplied and they uniquely identify the dataset, `myrror()` will proceed by joining the two datasets by the keys:

1.  **1:1** If the relationship between the two datasets is 1:1, `myrror()` will proceed by comparing the values of each matched row.

```{r}
myrror(survey_data, survey_data_3, by = c("country", "year"), interactive = FALSE)
```

2.  **m:1, 1:m** If the relationship between the two datasets is not 1:1 (i.e. there are multiple rows in one dataset that match a single row in the other dataset), `myrror()` will ask the user whether they want to proceed. If the user chooses to proceed, `myrror()` will join the two datasets by the keys and then compare the values of each matched row.

```{r}
myrror(survey_data, survey_data_1m, by = c("country", "year"), interactive = FALSE)
```

3.  **m:m** If the relationship between the two datasets is m:m, `myrror()` will abort the comparison by default.

```{r, error = TRUE}
myrror(survey_data_1m_2, survey_data_1m, by = c("country", "year"), interactive = FALSE)
```

### Non-Identified

If the keys are supplied but they do not uniquely identify the dataset, `myrror()` will inform the user and ask whether they want to proceed:

1.  **proceed** If the user chooses to proceed, `myrror()` will join the two datasets by the keys and then compare the values of each matched row.
    -   **m:1, 1:m** As above, if the relationship between the two datasets is not 1:1, `myrror()` will ask the user whether they want to proceed. If the user chooses to proceed, `myrror()` will join the two datasets by the keys and then compare the values of each matched row.
    -   **m:m** If the relationship between the two datasets is m:m, `myrror()` will abort the comparison.
2.  **not proceed** If the user chooses not to proceed, `myrror()` will abort the comparison.

## Without keys supplied

Currently, `{myrror}` does not align rows based on row content (e.g. `{waldo}`). This means that if the user does not provide keys, the function will compare the two datasets based on row number only. As you might expect, this can lead to incorrect result, especially if there are discrepancies in the number of rows. This is why there are a series of warning which will make the user consider whether or not it is sensible to proceed.

### Different Number of Rows

By default, if no keys are supplied, and there is a different number of rows, the comparison will be aborted:

```{r, error=TRUE}
myrror(survey_data, survey_data_4, interactive = FALSE)
```

### Same Number of Rows

If no keys are supplied, there is the same number of rows,  and the dataset is identified (there are no duplicates):

#### Identified

1. **Possible Keys Found** First, `myrror()` will try to suggest two possible keys or combinations of keys. Then it will proceed combining the two dataset by row numbers.
2. **No Keys Found** If no keys are found, `myrror()` will proceed combining the two dataset by row numbers.

```{r}
myrror(survey_data, survey_data_2, interactive = FALSE)
```

### Non-Identified

If no keys are supplied, there is the same number of rows, and the dataset is not identified (there are duplicates), `myrror()` will inform the user and ask whether they want to proceed, if the user chooses to proceed, `myrror()` will join the two datasets by row number.

```{r}
row_to_duplicate <- sample(nrow(survey_data), 1)
survey_data_copy <- rbind(survey_data, survey_data[row_to_duplicate, ])
row_to_remove <- sample(setdiff(1:nrow(survey_data_copy), row_to_duplicate), 1)
survey_data_copy <- survey_data_copy[-row_to_remove, ]

myrror(survey_data, survey_data_copy, interactive = FALSE)
```


